Security Metrics for the Android Ecosystem

### 2015-07-23 spsm04-thomas.tex
Add a todolater for somethign we don't have time for now (quantifying overestimation and underestimation)

Unfortunately, there is no ground truth of OS version information.
However, we have collated the API version information that Google has published most months since 2009.\footnote{\url{http://androidvulnerabilities.org/play/historicplaydashboard}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the \da\ data on API versions are similar to the Google data on API versions then the \da\ data on OS versions should be representative.
We compared the data from Google and from \da\ and they are similar.
We analysed the difference between the API version data from \da\ and Google Play, normalising for days since the API version was released.
This shows that the \da\ data systematically overestimates the prevalence of new API versions and underestimates the prevalence of old API versions.
This means that the OS version information from \da\ is likely to be overestimating the prevalence of new OS versions and hence our results are likely to be conservative.

>>>>

Unfortunately, there is no ground truth of OS version information.
However, we have collated the API version information that Google has published most months since 2009.\footnote{\url{http://androidvulnerabilities.org/play/historicplaydashboard}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the \da\ data on API versions are similar to the Google data on API versions then the \da\ data on OS versions should be representative.
We compared the data from Google and from \da\ and they are similar.
We analysed the difference between the API version data from \da\ and Google Play, normalising for days since the API version was released.
This shows that the \da\ data systematically overestimates the prevalence of new API versions and underestimates the prevalence of old API versions.
This means that the OS version information from \da\ is likely to be overestimating the prevalence of new OS versions and hence our results are likely to be conservative.\todolater{Provide some numbers which quantify this}
